### 2023-09-07 main.tex
lkj

@@

\begin{equation}\label{GainCommutationQ}

@@

Using again 

@@

@@

i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute. This simplify formula \eqref{W-charges-Bad} as
	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
	\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
Therefore, we can generalize \eqref{Three-Relation} and find 
		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}\\&

@@

This can be written as

>>>>

\begin{equation}\label{Commuting-Charges}

@@

\begin{equation}\label{Diagonal-Q-void}

@@

Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges} and \eqref{ExDNB-charges} we obtain 
	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\&=B_{i}^{2L-1}\left\{B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})-2(D_{i,i}^{2L}+D_{N,N}^{2L}+2(D_{i,i}^{2L+1}-D_{N,N}^{2L+1}))\right)-2\sum_{\ell=0\;\ell\neq i}B_{\ell}^{2L-1}D_{\ell,i}\right\}\nonumber\\&
	\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
By using \eqref{Dij-ref}, \eqref{Dii-ref} and observing that 
\begin{equation}\label{D2Lp1}
	D_{i,i}^{2L+1}-D_{N,N}^{2L+1}=-2I
we have 
	&Q_{0}^{2L}B_{i}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber=\left(B_{i}^{2L-1}\right)^{2}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L})+8\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
that can be rewritten as \eqref{Two-Relation}.
\item \textit{Case 2}: $i\neq j$. Using \eqref{GoodRelation} we have
	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=\left\{B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})\right)+4B_{j}^{2L-1}\right\}\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
thus we have 
 &Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle=B_{j}^{2L-1}\left(Q_{0}^{2L}-2(D_{j,j}^{2L}+D_{N,N}^{2L})+4\right)\nonumber\\&B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
Using \eqref{ExQ0B-charges}, \eqref{ExDiB-charges}, \eqref{ExDNB-charges}, \eqref{Commuting-Charges} and \eqref{D2Lp1} we obtain 
	&Q_{0}^{2L}B_{j}^{2L-1}Q_{0}^{2L}B_{i}^{2L-1}|\Psi_{0}^{0}\rangle\nonumber\\=&B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{N,N}^{2L})+4-2D_{j,j}^{2L}-2(D_{N,N}^{2L}+D_{i,i}^{2L+1}-D_{N,N}^{2L+1})\right)\nonumber\\&\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-2(D_{i,i}^{2L}+D_{j,j}^{2L}+2D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle\nonumber
	B_{j}^{2L-1}B_{i}^{2L-1}\left(Q_{0}^{2L}-4(D_{1,1}^{2L}+D_{N,N}^{2L}+8)\right)\left(Q_{0}^{2L}-2(D_{1,1}^{2L}+D_{N,N}^{2L})\right)|\Psi_{0}^{0}\rangle
that can be written as \eqref{Two-Relation}. 

@@

\begin{equation}\label{Commutativity-Gained}

@@

i.e. $Q_{0}^{2L}B_{i}^{2L-1}$ and $Q_{0}^{2L}B_{j}^{2L-1}$ do commute.
For fixed $k_{1},\ldots,k_{N-1}\in \mathbb{N}_{0}$, \eqref{Two-Relation} and \eqref{Commutativity-Gained} allow to write 
\begin{equation}\label{k-times-QB}
		\prod_{\ell=1}^{N-1}\left(Q_{0}^{2L}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle=\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(Q_{0}^{2L}-2j(D_{11}^{2L}+D_{NN}^{2L})+4j(j-1)\right)|\Psi_{0}^{0}\rangle
Therefore, using \eqref{veryUsefulSeries}, we obtain
\begin{equation}\label{k-times-LQB}
		&\prod_{\ell=1}^{N-1}\left((\Lambda_{0}+\epsilon-Q_{0}^{2L})^{-1}B_{\ell}^{2L-1}\right)^{k_{\ell}}|\Psi_{0}^{0}\rangle\\=&\prod_{\ell=1}^{N-1}\left(B_{\ell}^{2L-1}\right)^{k_{\ell}}\prod_{j=1}^{k_{1}+\ldots+k_{N-1}}\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}+2j(D_{11}^{2L}+D_{NN}^{2L})-4j(j-1)\right)^{-1}|\Psi_{0}^{0}\rangle
 %This simplify formula \eqref{W-charges-Bad} as
%	W|\Psi_{0}^{0}\rangle=&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}\\&\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{1}\right\}^{k_{1}}\cdots\;\left\{\left(\Lambda_{0}+\epsilon-Q_{0}^{2L}\right)^{-1}B_{N-1}\right\}^{k_{N-1}}|\Psi_{0}^{0}\rangle
%\end{split}
%where 
	%\binom{k_{1}+\ldots+k_{N-1}}{k_{1},\ldots,k_{N-1}}=\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}}
Therefore, we find 
		W|\Psi_{0}^{0}\rangle =&\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots \Delta_{N-1}^{k_{N-1}}\frac{	(k_{1}+\ldots+k_{N-1})!}{k_{1}!\cdots k_{N-1}!}\\&

@@

Using \eqref{veryUsefulSeries} and \eqref{Diagonal-Q-void} we obtain 
